%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Manu Bhargav}{Srirangarajan}{
\href{mailto:manubhargav27@gmail.com}{manubhargav27@gmail.com} | \href{tel:+919964210799}{+91 996 421 0799}\\
\#2269\textbackslash1D, Vinobha Road, Jayalakshmipuram, Mysuru, KA 570012
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\sectionsep
\subsection{Visvesvaraya} 
\subsection{Technological} 
\subsection{University }
\descript{Bachelor of Engineering}
\descript{Information Science}
\location{July 2016  |  Mysuru, KA}
Vidyavardhaka College of Engineering \\ 
Consistently ranked in \textbf{Top 3\%} \\
First Class with Distinction\\
\sectionsep

\sectionsep
\subsection{Udacity}
\descript{Front-End Web Developer Nanodegree}
\location{Jan 2017 | AT\&T, Google, GitHub}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
LinkedIn://  \href{https://www.linkedin.com/in/manubhargav}{\bf Manubhargav} \\
Portfolio:// \href{https://manubhargav.github.io}{\bf manubhargav.github.io} \\
Github Repo:// \href{https://github.com/manubhargav}{\bf github.com/manubhargav} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills \& Interests}
\sectionsep
\location{Strong}
\textbullet{} Angular \\
\textbullet{}   TypeScript \\
\textbullet{} Git \\
\textbullet{} Scrum/Agile \\
\sectionsep
\location{Familiar}
\textbullet{} Spring Boot \\
\textbullet{} RESTful API \\
\textbullet{} Java \\
\textbullet{} Maven \\
\textbullet{} Node.js \\
\textbullet{} RxJS \\ 
\textbullet{} NPM \\
\textbullet{} AWS Lambda \\
\textbullet{} AWS S3 \\
\textbullet{} Bootstrap \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Compiler Design \\
Operating Systems \\
Software Engineering \\
Unix and Shell Programming \\
Advanced Computer Networks \\
Information and Network Security \\
Data Warehousing and Data mining  \\
{\footnotesize \textit{\textbf{(Thesis and Research Paper) }}} \\



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
\runsubsection{Infosys Limited}
\descript{| Senior Software Engineer }
\location{Jan 2018 – Present | Mysuru, KA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Modernized core online banking functionality for retail and business clients.
\item Implemented new features and reviewed TypeScript code on high quality, performant monolithic code repository on the Front-end.
\item Developed REST APIs using Spring Boot framework on the Back-end. 
\item Built and published Angular 9 Ivy libraries using ng-packagr tool.
\end{tightemize}
\sectionsep
\runsubsection{Infosys Limited}
\descript{| Software Engineer }
\location{Feb 2017 – Jan 2018 | Mysuru, KA}
\begin{tightemize}
\item Vendor-based banking platform for Enterprise customers.
\item Developed highly scalable, distributed system on a multi-repository  Angular code-base.Also, improved user's experience by revamping the application.
\item Implemented new features in a highly collaborative environment with Product managers, Product designers and UI/UX experts.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Technical Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Projects}
\runsubsection{Namma Metro Map} 
\descript{\href{https://manubhargav.github.io/NammaMetroMap/}{| Live Demo} }
\begin{tightemize}
\item Single page application that presents Metro Rapid Transit in Bengaluru.
\item Taught myself JavaScript MVC framework - KnockoutJS and jQuery.
\item Devised several MediaWiki APIs, GoogleMaps APIs using AJAX calls.  
\end{tightemize}
\sectionsep

\runsubsection{Frogger}
\descript{\href{https://manubhargav.github.io/frogger/}{| Play now} }
\begin{tightemize}
\item HTML5 Canvas powered video game developed using Object Oriented Principles on a custom Game loop engine.
\item Use the arrow keys to navigate towards the water. Avoid the bugs along the way!
\end{tightemize}
\sectionsep

\runsubsection{Whack-a-mole}
\descript{\href{https://manubhargav.github.io/Whack-a-mole/}{| Play now} }
\begin{tightemize}
\item A popular arcade game built with Vanilla JavaScript and CSS Animations.
\item Use the cursor to hit the heads of mechanical moles with a mallet as they pop up from holes quickly and repeatedly.
\end{tightemize}
\sectionsep

\runsubsection{Galeria}
\descript{\href{https://secret-coast-79189.herokuapp.com/}{| Live Demo} }
\begin{tightemize}
\item Full-stack CRUD application where users can showcase their art.
\item Built with Ruby - Sinatra, PostgreSQL and deployed on Heroku. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Leadership and Awards} 
\begin{tabular}{rll}
2012         & Ranked 1\textsuperscript{st}/50  & CBSE 12th Examinations\\
2014	     & Class Representative             & VVCE, Mysuru\\
2015	     & Youth Intercollege Fest          & VTU Belagavi\\
2016	     & Ranked 2\textsuperscript{nd}/60  & VTU Examinations\\


\end{tabular}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
\bibliographystyle{abbrv}
\bibliography{publications}
\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
